Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-18 appendix.tex
sup

\noindent\textbf{I. Further Improving Efficiency of HM}

Being able to gain a higher robustness at a lower training cost indicates a
higher efficiency.
%
As discussed in Sec.~3.1, one potential way to further improve the adversarial
training efficiency is to incorporate adversarial training acceleration methods
such as Free Adversarial Training (FAT)~\cite{freeat} (for classification) into
our DML adversarial training.

We have tried to direct adopt FAT for adversarial training of DML model.
%
According to our observation, the model (RN18 on CUB dataset) is still prone
to collapse because the FAT algorithm can be interpreted as to maintain
a universal (agnostic to sample) perturbation that can maximize the loss.
%
Simple workarounds such as decaying the perturbation does not address this
issue.

Thus, our conclusion is that a non-trivial modification is still required
to incorporate the idea of FAT into adversarial training of DML model.

On the other hand, ACT~\cite{robrank} has a different inner loss function to
the outer minimization problem, and hence result in different gradients in the
inner and outer problems.
%
In this way, the gradients cannot be reused by FAT.
%
Re-calculating the gradients we need would simply double the
computational cost of the algorithm and halves the efficiency gain from FAT.

@@

~\newline\textbf{II. More Appropriate Destination Hardness}

We drew the conclusion that ``adversarial triplets should remain Semihard''
based on the empirical experimental results in Tab.~2 in the manuscript.
%
However, a better choice for $H_\mathsf{D}$ may exist between ``Semihard''
and ``Softhard''.
%
Exploration of a better source triplet sampling strategy for adversarial
training, as well as a better hardness range for adversarial triplets
may also be a direction for further robustness improvement.
%
In the manuscript, we only use the existing sampling methods in order to focus
on our contributions.

@@

It is unknown how defense methods for DML relates to the classification defense
task.
%
DML is closely related to self-supervised learning.
%
It is also unknown if a defense for the supervised learning scenario will
inspire the defense for unsupervised robust feature learning.

>>>>

\noindent\textbf{I. Faster Adversarial Training with HM}

As discussed in Sec.~3.1, one potential adversarial training acceleration
method is to incorporate Free Adversarial Training (FAT)~\cite{freeat}
(originally for classification) into our DML adversarial training with HM.
%
Besides, directly incorporating FAT into the min-max adversarial training of
DML will easily result in model collapse as well, because the FAT algorithm can
be interpreted as to maintain a universal (agnostic to sample) perturbation
that can maximize the loss.
%
Thus, non-trivial modifications are still required to incorporate FAT FAT into
adversarial training with HM. This is left for future work.

@@

~\newline\textbf{II. Better Choice for Destination Hardness}

The proposed LGA function incorporates our empirical observation that
``adversarial triplets should remain Semihard'' based on the results in Tab.~2.
%
However, a better choice for $H_\mathsf{D}$ may exist between ``Semihard'' and
``Softhard'' that can achieve better overall performance.
%
In the manuscript, we only use the existing sampling methods and simple
pseudo-hardness functions in order to avoid distraction from our focus.

@@

It is unknown whether DML defenses will improve the robustness in the
classification task.
